Inferring Graphics Programs from Images

### 2017-05-12 paper.tex
small changes

This network suffices to ``derender'' images like those shown in
Figure~\ref{trainingData}.  We can perform a beam search decoding to
recover what the network thinks is the most likely execution trace for
images like these. But, if the network makes a mistake (predicts an
incorrect line of code), it has no way of recovering from the error.
In order to derender an image with $n$ objects, it must correctly
predict $n$ drawing commands -- so is probability of success will
decrease exponentially in $n$.  For added robustness as $n$ becomes
large, we treat the neural network outputs as proposals for a SMC
sampling scheme.  For the SMC sampler, we use pixel wise distance as a
surrogate for a likelihood function; see
supplement. Figure~\ref{syntheticResults} compares the neural network
with SMC against the neural network by itself or SMC by itself.  Only
the combination of the two passes a critical test of generalization:
when trained on images with $\leq 8$ objects, it successfully parses
scenes with many more objects than the training data.

@@

\subsection{Generalizing to hand drawings}
We believe that converting synthetic, noiseless images into a restricted subset of
\LaTeX has limited usefulness.  A more practical
application is one that extends to hand drawings.  We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we used graph paper.
\begin{figure}[H]%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
    \subcaption{}
  \end{minipage}
  \caption{(a): a hand drawing. (b): Rendering of the parse our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\label{handDrawingExamples}
\end{figure}

@@

\begin{table}
  \begin{tabular}{rl}
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
  \end{table}

>>>>

This network suffices to ``derender'' images like those shown in
Figure~\ref{trainingData}.  We can perform a beam search decoding to
recover what the network thinks is the most likely execution trace for
images like these. But, if the network makes a mistake (predicts an
incorrect line of code), it has no way of recovering from the error.
In order to derender an image with $n$ objects, it must correctly
predict $n$ drawing commands -- so its probability of success will
decrease exponentially in $n$, assuming it has any nonzero chance of
making a mistake.  For added robustness as $n$ becomes large, we treat
the neural network outputs as proposals for a SMC sampling scheme.
For the SMC sampler, we use pixel wise distance as a surrogate for a
likelihood function; see supplement. Figure~\ref{syntheticResults}
compares the neural network with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 8$
objects, it successfully parses scenes with many more objects than the
training data.

@@

\subsection{Generalizing to hand drawings}
We believe that converting synthetic, noiseless images into a restricted subset of
\LaTeX has limited usefulness.  A more practical
application is one that extends to hand drawings.  We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we made the drawings on graph paper.
\begin{figure}[H]%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
    \subcaption{}
  \end{minipage}
  \caption{(a): a hand drawing. (b): Rendering of the parse our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\label{handDrawingExamples}
\end{figure}

@@

\begin{table}[h]
  \begin{tabular}{rl}
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
  \end{table}
